### 2020-01-26 conclusions.tex
Fixups

As future work, we would like to further validate our approach and
improve our admittedly \emph{ad hoc} mutant distance metric.  Allowing
user feedback \cite{EndUserMistake,OnlyOracle}, or applying metric
learning methods \cite{kulis2012metric} (particularly unsupervised
learning \cite{scholkopf1998nonlinear,tipping1999probabilistic}) are
the most obvious and interesting possibilities for a better metric.
Finally, mutant prioritization should be applicable to improving
software testing, as well \cite{groce2018verified}.  We are also interested in combining static analysis and testing mutation analysis: it might be useful to consider a mutant killed if it is detected either by static or dynamic analysis, using static kills to lower the number of required costly testing/verification runs for mutants and the combined result as a useful guide to the quality of overall \emph{defense in depth} for high-importance code.

>>>>

As future work, we would like to further validate our approach and
improve our admittedly \emph{ad hoc} mutant distance metric.  Allowing
user feedback \cite{EndUserMistake,OnlyOracle}, or applying metric
learning methods \cite{kulis2012metric} (particularly unsupervised
learning \cite{scholkopf1998nonlinear,tipping1999probabilistic}) are
the most obvious and interesting possibilities for a better metric.
Finally, mutant prioritization should be applicable to improving
software testing, as well \cite{groce2018verified}.  We are also interested in combining static and traditional mutation analysis: it might be useful to consider a mutant killed if it is detected either by static or dynamic analysis, using static kills to lower the number of required costly testing/verification runs for mutants, and the combined result as a useful guide to the quality of overall \emph{defense in depth} \cite{antunes2012defending,FC20} for high-importance code.

### 2020-01-26 experiments.tex
Fixups

For Java and Python, we did not have to worry about invalidating tool improvements by basing our results on benchmark code.  We therefore aimed to use realistic, important source code.  We selected top GitHub projects (defined by number of stars) for each language, and removed projects with fewer than 5 developers or less than six months of commit history (as well as projects that did not build).  For Java, we analyzed the top 15 projects satisfying our criteria, with a maximum of 623,355 LOC and a minimum of 3,957 LOC, and a total size of 1.8 million LOC.  Because the Universal Mutator does not ``know'' Java syntax, the Java compiler rejected a large number of the generated mutants (e.g., deleting definitions or declarations), leaving us with just over 70,000 mutants to analyze, ranging from 136 to 10,016 per project.

>>>>

For Java and Python, we did not have to worry about invalidating tool improvements by basing our results on benchmark code.  We therefore aimed to use realistic, important source code.  We selected top GitHub projects (defined by number of stars) for each language, and removed projects with fewer than 5 developers or less than six months of commit history (as well as projects that did not build).  For Java, we analyzed the top 15 projects satisfying our criteria, with a maximum of 623,355 LOC and a minimum of 3,957 LOC, and a total size of 1.8 million LOC.  Because the Universal Mutator does not ``know'' Java syntax, and Java is very verbose, the Java compiler rejected a large number of the generated mutants (e.g., deleting declarations), leaving just over 70,000 mutants, ranging from 136 to 10,016 per project.

### 2020-01-26 introduction.tex
Fixups

Consider the code in Figure \ref{fig:sol424intro}, from the Solidity 0.4.24 ``Introduction to Smart Contracts''.  The Universal Mutator tool \cite{universalmutator,regexpMut}, which has been extensively tuned for Solidity's grammar (though not to target any particular vulnerabilities), and is the only smart contract mutation tool referenced in the Solidity documentation (\url{https://solidity.readthedocs.io/en/v0.5.12/resources.html}), produces seven valid, non-redundant (by Trivial Compiler Equivalence \cite{TCE}) mutants for this trivial example code.  Both the public version of Slither \cite{slither} and SmartCheck \cite{smartcheck} produce a small number (three and two, respectively) of low-severity, informational, warnings for this code.  Both tools also detect (by increasing the number of warnings produced) four of the seven mutants.  However, only one of the mutants detected is common to both tools: both tools detect changing the {\tt return} statement in the {\tt get} function to a call to {\tt selfdestruct} the smart contract.  Slither, but not SmartCheck, also detects replacing the assignment of {\tt storedData} in {\tt set} with either a {\tt selfdestruct} or {\tt revert}, or simply removing it altogether.  SmartCheck, on the other hand, detects removing the {\tt return} in {\tt get} or replacing it with a {\tt revert}, or removing the {\tt public} visibility modifier for {\tt get} \footnote{Slither's ``missing return'' detector is only available in the private version of slither, or through the {\tt crytic} service provided by Trail of Bits.}.  If we restrict our analysis to findings with a severity greater than informational, SmartCheck detects no mutants of the contract, while Slither still reports that some mutants \emph{allow an arbitrary caller to cause the contract to self destruct}.  This simple example shows how our approach works on a small scale.  Using large numbers of larger, more realistic contracts makes it possible to extract the same kind of information, on a much larger scale.  Prioritization of mutants is not very useful here (ranking three mutant saves little effort), so we will show the utility of that approach in our full Solidity results.

>>>>

Consider the code in Figure \ref{fig:sol424intro}, from the Solidity 0.4.24 ``Introduction to Smart Contracts''.  The Universal Mutator tool \cite{universalmutator,regexpMut}, which has been extensively tuned for Solidity's grammar (though not to target any particular vulnerabilities), and is the only smart contract mutation tool referenced in the Solidity documentation (\url{https://solidity.readthedocs.io/en/v0.5.12/resources.html}), produces seven valid, non-redundant (by Trivial Compiler Equivalence \cite{TCE}) mutants for this trivial example code.  Both the public version of Slither \cite{slither} and SmartCheck \cite{smartcheck} produce a small number (three and two, respectively) of low-severity, informational, warnings for this code.  Both tools also detect (by increasing the number of warnings produced) four of the seven mutants.  However, only one of the mutants detected is common to both tools: both tools detect changing the {\tt return} statement in the {\tt get} function to a call to {\tt selfdestruct} the smart contract.  Slither, but not SmartCheck, also detects replacing the assignment of {\tt storedData} in {\tt set} with either a {\tt selfdestruct} or {\tt revert}, or simply removing it altogether.  SmartCheck, on the other hand, detects removing the {\tt return} in {\tt get} or replacing it with a {\tt revert}, or removing the {\tt public} visibility modifier for {\tt get} \footnote{Slither's ``missing return'' detector is only available in the private version of slither, or through the {\tt crytic} service provided by Trail of Bits.}.  If we restrict our analysis to findings with a severity greater than informational, SmartCheck detects no mutants of the contract, while Slither still reports that some mutants \emph{allow an arbitrary caller to cause the contract to self destruct}.  This simple example shows how our approach works on a small scale.  Using large numbers of larger, more realistic contracts makes it possible to extract the same kind of information, on a much larger scale.  Prioritization of mutants is not very useful here (ranking three mutants saves little effort), so we will show the utility of that idea in our full Solidity results.
